Paper_stuff

### 2024-01-30 Paper_stuff.Rmd
Adding new RMD with stuff just for LAsso responder paper

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                          "0"="<Grade 12",
                          "1"="<Grade 12",
                          "2"="HS Diploma or GED",
                          "3"="HS Diploma or GED",
                          "4"="Some College/Associates Degree",
                          "5"="Some College/Associates Degree",
                          "6"="Bachelors Degree",
                          "7"="Bachelors Degree",
                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                          "0"="Female",
                          "1"="Male",
                          "2"="Non-Binary",
                          "3"="Other",
                          "4"="Other"),
                     Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                          "0"="Married or Cohabitating",
                          "1"="Married or Cohabitating",
                          "2"="Widowed or Separated",
                          "3"="Widowed or Separated",
                          "4"="Divorced",
                          "5"="Single or Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                          "1"="Straight",
                          "2"="Gay",
                          "3"="Bisexual",
                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                          "0"="General",
                          "1"="Trauma",
                          "2"="Young Adult",
                          "3"="BPD"),
                     Race_1 = ifelse(Race_1 == 6, NA, Race_1),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other",
                                      "11"="Other",
                                      "17"="Other",
                                      "0" ="Other"),

@@

                                Trauma_C == 1 & Psychotic_D ==1, 1, 0))
  )

@@

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")

@@

Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
      Depression_Responder = as.factor(recode(Depression_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
         Depression_Responder = as.factor(recode(Depression_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
         Anxiety_Responder = as.factor(recode(Anxiety_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    RESPONDER_FIGS = as.factor(
        ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
        ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
        )))

@@

# Results
### The overall breakdown of patients’ demographics and diagnoses. 
Table – Demographics
Table – Diagnoses
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1)
        )

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Total Sample")
view(Demo_tab)

#Disorder Table - duratin
Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_post))
                                       #Mothership_Diag_treat))
colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
Dis_tab

#Disorder Tab by 10 days
Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_post))
                                      #Mothership_Diag_treat))
colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
Dis_tab_10

##### Add other demographic information here

@@

Dumbell Plot by Disorder
```{r}
AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$pre_anx,
                                  Mothership_post$post_anx,
                                  Mothership_post$pre_dep,
                                  Mothership_post$post_dep,
                                  Mothership_post$RESPONDER_FIGS)) 
  # filter(!is.na(Mothership_post$Disorder_Type))
colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","RESPONDER_FIGS)")

### Overall Plot
```{r}
# Pre Post CUDOS/CUXOS Plot
ggplot(data=AnxDep_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5)+
  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

@@

#### ANX
ggplot(data=ANX_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUXOS Score")+
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

#### DEP
ggplot(data=DEP_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=as.factor(Disorder_Type),color=as.factor(Disorder_Type)))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS Score")+
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self report depression was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

### FACAT WRAP

@@

@@

# #Create a New Data Set with an Average Anxiety Variable
# Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
#   group_by(TxDay) %>%
#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#plot Anxiety mean with each group

# New dataset for the treatment duration Anxiety plot
Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_Mean_CUXOS2 <- Mothership_Long_anx %>%
  group_by(Duration,RESPONDER_FIGS,TxDay) %>%
  summarise(Score=mean(CUXOS,na.rm=TRUE))

@@

@@

@@

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
  geom_bar()+ #fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"))+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,2100)) +
  #scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  coord_flip() +
  facet_wrap(~Duration,labeller = labeller(Duration =
      c("1" = "1-5 Days", 
        "2" = "6-10 Days", 
        "3" = "11-15 Days",
        "4" = "16+ Days")
      ))

@@

ggplot(data = subset(Mothership_post, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
  coord_flip()
```

@@

>>>>

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                          "0"="<Grade 12",
                          "1"="<Grade 12",
                          "2"="HS Diploma or GED",
                          "3"="HS Diploma or GED",
                          "4"="Some College/Associates Degree",
                          "5"="Some College/Associates Degree",
                          "6"="Bachelors Degree",
                          "7"="Bachelors Degree",
                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                          "0"="Female",
                          "1"="Male",
                          "2"="Non-Binary",
                          "3"="Other",
                          "4"="Other"),
                     Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                          "0"="Married or Cohabitating",
                          "1"="Married or Cohabitating",
                          "2"="Widowed or Separated",
                          "3"="Widowed or Separated",
                          "4"="Divorced",
                          "5"="Single or Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                          "1"="Straight",
                          "2"="Gay",
                          "3"="Bisexual",
                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                          "0"="General",
                          "1"="Trauma",
                          "2"="Young Adult",
                          "3"="BPD"),
                     Race_1 = ifelse(Race_1 == 6, NA, Race_1),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1" ="Treatment Complete",
                                      "2" ="Treatment nearly complete",
                                      "3" ="Insurance no longer covering",
                                      "4" ="Nonattendance",
                                      "5" ="Inappropriate (language)/Referred to another tx setting",
                                      "6" ="Transferred to inpatient",
                                      "7" ="Withdrew due to external limitations",
                                      "8"= "Withdrew AMA",
                                      "9"= "Other",
                                      "10"="Other",
                                      "0" ="Other"),
                    Referral_1 = as.factor(Referral_1),
                    Referral_1 = recode(Referral_1,
                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "17"="Other",
                                      "0" ="Other"),

@@

                                Trauma_C == 1 & Psychotic_D ==1, 1, 0)),

          #this isn't working???
                  # Sum_DX = #Primary
                  #       as.integer(Mood_D) + as.integer(Anxiety_D) +as.integer(OCD_P) + 
                  #       as.integer(BPD_P) + as.integer(Substance_D) + as.integer(Trauma_D) + 
                  #       as.integer(Psychotic_D) + as.integer(Eating_D) + as.integer(Somatic_D) + as.integer(Other) +
                  #          #Co-Occurring
                  #       as.integer(GAD_C) + as.integer(Panic_C) + as.integer(PanicAgor_C) + as.integer(Agoraphobia_C) + 
                  #       as.integer(Social_C) + as.integer(Specific_C) + as.integer(MDD_C) + as.integer(Bipolar1_C) + as.integer(Bipolar2_C) + 
                  #       as.integer(Dysthymia_C) + as.integer(Alcohol_C) + as.integer(Drug_C) + as.integer(PTSD_C) + 
                  #       as.integer(Adjustment_C) + as.integer(Schiz_C) + as.integer(Schizaff_C) + as.integer(Anorex_C) + as.integer(Bulim_C) + 
                  #       as.integer(Binge_C) + as.integer(Somat_C) + as.integer(UndiffSoma_C) + as.integer(Hypochondriasis_C) + as.integer(OCD_Co_C) + 
                  #       as.integer(BPD_Co_C)
                      )

View(Mothership)

@@

@@

Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
      Depression_Responder = as.factor(recode(Depression_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
         Depression_Responder = as.factor(recode(Depression_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
         Anxiety_Responder = as.factor(recode(Anxiety_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    RESPONDER_FIGS = as.factor(
        ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
        ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
        ))) |>
  filter(!is.na(RESPONDER_FIGS))

@@

# Results

Part 1 - treatment information

- demographics breakdown
- treatment breakdown
    - duration of stay based upon disorder?
    - mean anx / depression based upon stay
- Treatment discharge?
- pre post by responder non responder

### The overall breakdown of patients’ demographics and diagnoses. 
Table – Demographics
Table – Diagnoses
Table - Treatment information
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),
         !is.na(RESPONDER_FIGS)
        )

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
Demo_tab

# Treatment info
resp_tab <- data.frame(table1::table1(
  ~IPT_track_1 + Days_complete_1 + DC_status_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 + Current_Dx | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab
```

## Pre Post
### table - prepost
```{r}

@@

### Pre-post Line Plot
```{r}

@@

#3. Create a combined dataset

@@

summary(Mothership_post$Duration_lab)
test <- Mothership_post |>
  filter(
Duration == 2
)

@@

# #Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
```

FIGURE OUT WHY THIS SHIT ISN'T WORKING IT IS GRABBING VALUES THAT DOEN'T EXIST
ITS GRABBING VALUES (CUXOS) FOR PEOPLE THAT DISCHARGED. I DON'T UNDERSTAND HOW THIS WORKS
```{r}
Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
View(Mothership_duration_CUXOS)

Mothership_duration_CUXOS[6:20,3] = NA
Mothership_duration_CUXOS[37:41,3] = NA
Mothership_duration_CUXOS[74:83,3] = NA
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
Mothership_duration_CUXOS

```{r}
#plot Anxiety mean with each group

Mothership_Long_anx$Duration_lab

# New dataset for the treatment duration Anxiety plot
Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
  group_by(Duration_lab,TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_Mean_CUXOS2 <- Mothership_Long_anx %>%
  group_by(Duration_lab,RESPONDER_FIGS,TxDay) %>%
  summarise(Score=mean(CUXOS,na.rm=TRUE))

@@

View(Mothership_Mean_CUXOS)

@@

ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration_lab,color=Duration_lab))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
  scale_color_manual(values=c("#BB9D00","red",
                              "darkred","orange"))+
  theme(panel.background=NULL)+
  labs(subtitle = "Broken up by Duration of Treatment")
```

@@

@@

ggplot(data = subset(Mothership_post, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
  coord_flip()

@@

tables
```{r}
  ### To univariate tests with these???

#Disorder Table - duratin
# Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_post))
#                                  #Mothership_Diag_treat))
# colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
# Dis_tab

#Disorder Tab by 10 days
# Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_post))
# colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
# Dis_tab_10

# Disorder by responder
```

Dumbell Plot by Disorder - Pre and Post
```{r}
AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$pre_anx,
                                  Mothership_post$post_anx,
                                  Mothership_post$pre_dep,
                                  Mothership_post$post_dep,
                                  Mothership_post$RESPONDER_FIGS)) 
  # filter(!is.na(Mothership_post$Disorder_Type))
colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","RESPONDER_FIGS)")

### Dumbell Plot by Disorder
```{r}
Pre_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Pre")

ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+

  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```

Overall plot - pre post
```{r}
# Pre Post CUDOS/CUXOS Plot
# ggplot(data=AnxDep_PrePost_mean,
#        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
#            group=Test,color=fct_rev(Test)))+
#   geom_point(size=2.5)+
#   geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
#   scale_x_discrete(name="Time Point")+
#   scale_y_continuous(name="CUDOS/CUXOS Score")+
#   ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
#   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   theme(legend.title = element_blank())
```

pre post disorder
```{r}
#### ANX
# ggplot(data=ANX_PrePost_mean,
#        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
#            group=Disorder_Type,color=Disorder_Type))+
#   geom_point(size=2.5)+
#   geom_line(size=1)+
#   scale_x_discrete(name="Time Point")+
#   scale_y_continuous(name="CUXOS Score")+
#   labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
#        subtitle = "Self Report anxiety was assessed using the CUXOS",
#        caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
#   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   theme(legend.title = element_blank())

#### DEP
# ggplot(data=DEP_PrePost_mean,
#        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
#            group=as.factor(Disorder_Type),color=as.factor(Disorder_Type)))+
#   geom_point(size=2.5)+
#   geom_line(size=1)+
#   scale_x_discrete(name="Time Point")+
#   scale_y_continuous(name="CUDOS Score")+
#   labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
#        subtitle = "Self report depression was assessed using the CUDOS",
#        caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
#   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   theme(legend.title = element_blank())
```

```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

 #CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))

ggplot(Mothership_post, aes(x = Treatment_Responder)) +
  geom_bar() +
  coord_flip() +
  scale_x_discrete(limits =c("Low Baseline", "Both Worse", "Dep Worse", "Anx Worse","Both Unresponder","Dep Unresponders", "Anx Unresponders","Both_Responder", "Anx Responder","Dep Responder"))+
  labs(
    title = "Treatment response of Anxiety and Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

ggplot(Mothership_post, aes(x = Anx_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Anxiety",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

ggplot(Mothership_post, aes(x = Dep_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")
```

# Pie Chart For Education Status 
We wanted to learn how to make a pie chart in R so here is one!
```{r}
#Create Table and Data Frame
Education<-table(Mothership_post$Education_1)
Education_df<-as.data.frame(Education)
Education_df

#Rename Columns
colnames(Education_df)[1]="Category"
colnames(Education_df)[2]="Frequency"

Education_df$Category=recode(Education_df$Category,
                             "0"="<Grade 6", 
                             "1"="Grades 7-12",
                             "2"="HS Diploma", 
                             "3"="GED",
                             "4"="Some College",
                             "5"="Associates Degree",
                             "6"="Bachelors Degree",
                             "7"="Some Grad School",
                             "8"="Grad Degree")

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()
```

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
  geom_bar()+ #fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"))+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,2100)) +
  #scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  coord_flip() +
  facet_wrap(~Duration,labeller = labeller(Duration =
      c("1" = "1-5 Days", 
        "2" = "6-10 Days", 
        "3" = "11-15 Days",
        "4" = "16+ Days")
      ))
```
